### 2018-03-20 Writing/draft.tex
Comments on conclusion

\subsection{Conclusion}
Correlation between characters can be induced through three main phenomenon: intra-organismal features, evolutionary history or biases in coding the characters.
Although one could argue (righteously!) that coding induced correlation is easily avoidable and that intra-organismal and evolutionary correlations are actually at the core of evolutionary biology, in the age of ever expanding morphological matrices \citep[e.g.][with more than 1000 characters each]{nithe2013,O'Leary08022013}, we can expect the dependence between characters to increase stochastically.
Moreover, because phylogenetic inference software are unable to \textit{a priori} differentiate these difference correlations, it is important to understand to what extant topologies can be induced by such bias.

We found that character differences as a proxy for character correlation have a strong effect on the recovering the ``normal'' topology: when character correlation was high (low character differences), the topology was always the furthest away from the ``normal'' topology.
Conversely, when correlation between characters was low, the topology was always the closest to the ``normal'' topology.
These results seems independent on the size of the matrix (number of taxa and/or characters) but can be influenced by the phylogenetic inference method used with Bayesian inference faring better in terms of clade conservation, especially in larger matrices.

However, in modest size matrices (25 taxa 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
We hope that these results will encourage researchers working on discrete morphological characters to continue exploring morphology through discrete characters to better understand the Tree of Life.

>>>>

\subsection{Conclusion}
Correlation between characters can be induced through three main phenomena: intra-organismal relationships, selection-driven covariation or biases in coding the characters.
Although one could argue that coding-induced correlation is easily avoidable and that intra-organismal and evolutionary correlations are actually at the core of evolutionary biology, in the age of ever expanding morphological matrices \citep[e.g.][with more than 1000 characters each]{nithe2013,O'Leary08022013}, we can expect the dependence between characters to increase stochastically.
% I have no idea what thae above sentence means.
Moreover, because phylogenetic inference software are unable to \textit{a priori} differentiate these difference correlations, it is important to understand to what extant topologies can be induced by such bias.

We found that character differences as a proxy for character correlation have a strong effect on recovering the ``normal'' topology: when character correlation was high (low character differences), the topology was always the furthest away from the ``normal'' topology.
Conversely, when correlation between characters was low, the topology was always the closest to the ``normal'' topology.
These results seem independent on the size of the matrix (number of taxa and/or characters) but can be influenced by the phylogenetic inference method used with Bayesian inference faring better in terms of clade conservation, especially in larger matrices.

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
% But at what point? How much correlation is needed to affect it?
We hope that these results will encourage researchers working on discrete morphological characters to continue exploring morphology through discrete characters to better understand the Tree of Life.
% This line sounds like something from an undergraduate term paper.
